System Architecture for a Class of Small Service Vehicle

### 2015-12-15 ieee-pandoc-template/paper.tex
continue writing towards IVS2015

{[}XME? Please fill in{]}

@@

\section{Safety Consideration}\label{safety-consideration}

Safety is very important in a critical mission project like autonomous
service vehicle. Not only that robust operation is required, but also
human safety must be prioritized in the system logic. Some components in
the system that needs attention are listed in Table \ref{table_example}.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{A Simple Example Table, IEEE standard format}
\label{table_example}
\centering
\begin{tabular}{c||c}
\hline\bfseries Component & \bfseries Risk\\
\hline
\hline Drive-By-Wire & Malfunction of motors\\
\hline
\hline GPS & GPS denied\\
\hline
\hline Camera & Cable loose\\
\hline
\end{tabular}
\end{table}

>>>>

Middleware refers to the software component that connects the various
modules across network distributed system. It makes communication
transparent to connected modules by providing reliability, consistency,
security, and privacy capabilities. In our architecture
CHROMOSOME\citep{CHROMOSOME} a Message-oriented middleware is used.
CHROMOSOME implements publish-subscribe message paradigm, which also
provides more guarantees with respect to the behaviour of distributed
applications. \citep{buckl2014chromosome} The other alternative
middlewares are Robotics Operating System (ROS) \citep{quigley2009ros}
and OpenRTM-aist \citep{ando2005rt} which are commonly used in the field
of Robotics.

@@

..Or, using numbering and some examples of referencing them given above.

\subsection{Path Planning}\label{path-planning-1}

Citations examples\ldots{}

\subsection{Control}\label{control-1}

Vehicle control or autonomous navigation is one of the key component for
autonomous vehicle. Vehicle control performs necessary action to follow
the intended path generated by path planner for smoother navigation
towards destination point. The gas, brake control for longitudinal
direction will be handled by velocity control and the steering control
for turning across lateral direction will handled by lateral control
module.

\subsubsection{Velocity control}\label{velocity-control}

Velocity control will estimate the gas, brake motor position in the
drive by wire system for maintaining the desired velocity and braking
for the vehicle. The desired velocity of the vehicle is determined with
the modules input such as path planning, obstacle detection and health
monitoring system. For autonomous lateral control the fixed constant
velocity will not be a wise choice, since the navigation path is not
always straight line of travel. The path may consists of various turns
and unexpected circumstances like obstacles. For smoother path following
and avoid jerkiness of vehicle, speed profiling have to done based on
path curvatures and speed limits. Based on the data collected by manual
driving, the speed is calculated for various path curvatures (turns).
During the local path generation, the curvature of path is calculated
and desired speed will be assigned to each curvatures across the path.
To avoid rapid speed change and to make velocity transition smooth from
straight line to curvature areas velocity averaging is performed in the
direction of end to path start. Apart from speed determined by speed
profiler across the path, in event of obstacle detection vehicle will
also perform action like slow down or stops based on obstacle detected
distance. In the event of certain module error or network communication
failure, health monitoring system will perform stop action based on
severity of error. To achieve desired velocity, the controller need to
calculate the desired gas/brake position of the motor. Thus one of the
frequently used controller technique closed loop PID controller is
implemented. The closed loop PID controller helps in noise rejection and
robustness of control with design flexibility. Based on desired
velocity, the controller will calculate the motor position and passes to
drive by wire (DBW) system. Drive by wire system will convert controller
command to control signal and passes to the motor. The wheel encoder
will help to measure the speed precisely and feedback to the controller
for the necessary action. The block diagram of the velocity control
implementation is shown in Fig \ref{fig_vel_control}.

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{pid_velocity.pdf}
\caption{Velocity control based on closed loop PID.}
\label{fig_vel_control}
\end{figure}

\subsubsection{Lateral Control}\label{lateral-control}

Lateral control aims to control the steering angle of the vehicle based
on trajectory generated by path planner. In our study we have developed
lateral controller based on Stanley's \citep{ventures2006stanley}
steering controller. Stanley steering controller is one of the popular
geometric path tracking approach used by Stanford university's
autonomous vehicle during DARPA grand challenge 2006. he closed-loop
geometric tracking controller helps vehicle to follow the desired path
generated by path planning. The controller is based on non-linear cross
track error \(C_{e}\) and heading error \(\theta_{e}\). Cross track
error is the lateral distance between front axle center point (P\_\{x\},
P\_\{y\}) and closest reference point (R\_\{x\}, R\_\{y\}) for which
exponential can be shown\citep{ventures2006stanley}. This term helps the
vehicle to steer towards the path to yield \(C_{e}\) as zero when its
following the path. The heading error \(\theta_{e}\) is calculated by
difference in vehicle heading \(\theta\) and reference heading
\(\theta_{r}\) of path at \((R_{x}, R_{y})\). This term error directly
apply to steering angle \(\delta\) with some steering angle limitation.

\begin{equation}
\label{eqn_heading_error}
\theta_{e} = \theta - \theta_{r}
%\caption{Heading error}
\end{equation}

When the cross track error \(C_{e}\) is non-zero, it adjusts \(\delta\)
such that the intended trajectory intersects the reference path tangent
from \((R_{x}, R_{y})\) at velocity in time \(V_{t}\) units from the
front axle center point \((P_{x}, P_{y})\). The resulting steering
control law by combining two terms are shown in equation
\ref{eqn_stanley_equation} below. The figure \ref{fig_stanley}
illustrates the geometric relationship of control parameters.

\begin{equation}
\label{eqn_stanley_equation}
\delta(t) = k_{h}\theta_{e} + tan^{^{-1}}\left (\frac{k_{c}C_{e}(t)}{V_{x}(t)}  \right )
\end{equation}

Fig ?? shows a control error during simulation. A Stanley controller can
be used for different type of course, such as parking, low speed, and
medium travels.

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{stanley_2.pdf}
\caption{Stanley controller geometry}
\label{fig_stanley}
\end{figure}

\section{Health Monitoring}\label{health-monitoring}

Safety is very important in a critical mission project like autonomous
service vehicle. Not only that robust operation is required, but also
human safety must be prioritized in the system logic. Some components in
the system that needs attention are listed in Table \ref{table_risk_hm}.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Risk in safety assessment for health monitoring module}
\label{table_risk_hm}
\centering
\begin{tabular}{c||c}
\hline\bfseries Component & \bfseries Risk\\
\hline
\hline Drive-By-Wire & Malfunction of motors\\
\hline
\hline GPS & GPS denied\\
\hline
\hline Camera & Cable loose\\
\hline
\end{tabular}
\end{table}
